### 2013-11-16 Paper_Markdown.Rmd
Added text to the document, cleaned up some extra lines in the bootstrap_mat.R, no actual code changes.

**Abstract**
Some jibberish.

@@

Introduction
=========================
Pollen assemblages are widely used for paleoclimatic reconstruction during the Holocene, but this method is also applied to pollen assemblages from the last Glacial period (Bartlein et al., 2011), as well as to earlier pollen assemblages, such as those during the Eemian (Brewer et al, 2008).  A particular challenge for climate reconstruction using these much earlier samples is the presence of non-analogue vegetation.  Non-analogue pollen assemblages pose a problem for many reconstruction techniques, these vegetation assemblages may be the result of sets of climate variables that no longer co-exist, ecological conditions resulting from differing rates of species migration or release from herbivores (Gill et al., 2009?), or as a result of changes in human land use (St. Jacques?, maybe not the best. . .).

@@

dissim.scores <- data.frame(dissim = c(min.diss, 
                                       max.diss, 
                                       as.vector(dists)[sample(length(dists), 10000)]),
                            class   = c(rep('Minimum', length(min.diss)),
                                        rep('Maximim', length(max.diss)), 
                                        rep('All', 10000)))

@@

non.ana.map <- ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_path(aes(group=group), color='black') +
  geom_point(data = data.frame(climate)[mds$non.ana == FALSE,], 
             aes(x = LONDD, y = LATDD), alpha=0.5) +
  geom_point(data = data.frame(climate)[mds$non.ana == TRUE,], 
             aes(x = LONDD, y = LATDD), color = 'red') +
   theme_bw() +
  coord_map(projection='albers', lat0=30, lat1=50, xlim=c(-140, -60), ylim=c(26, 75))

@@

```{r LoadOutputs, echo=FALSE, message=FALSE, warning=FALSE}
load('data/wa.res.RData')
load('data/mat.res.RData')
load('data/wapls.res.RData')

vals <- c(seq(0, 0.2, by=0.001), seq(0.21, 1, by=0.01))

>>>>

**Abstract**
Fossil pollen provides a widespread proxy for past vegetation.  It is increasingly used in paleoclimatic reconstruction, but the limits of its utility are not well known.  Methodological advances, such as the development of tests for spatial autocorrelation, and newer methods for climate reconstruction using boosted regression trees may improve the abilities of these climate reconstruction techniques, but little is known about the accuracy of these models under conditions of non-analogue vegetation known to occur at the end of the late glacial.  In this paper we generate non-analogue pollen assemblages by excluding close neighbours from calibration datasets at increasingly larger squared chord distances.  Using three standard and two newer techniques we then test the ability of pollen-based climate models to accurately recostruct climate under conditions of no-analogue vegetation.

@@

Introduction
=========================
Pollen assemblages are widely used for paleoclimatic reconstruction during the Holocene, but this method is also applied to pollen assemblages from the last Glacial period (Bartlein et al., 2011), as well as to earlier pollen assemblages, such as those during the Eemian (Brewer et al, 2008).  A particular challenge for climate reconstruction using these much earlier samples is the presence of non-analogue vegetation.  Non-analogue pollen assemblages pose a problem for many reconstruction techniques, these vegetation assemblages may be the result of sets of climate variables that no longer co-exist, ecological conditions resulting from differing rates of species migration or release from herbivores (Gill et al., 2009), or as a result of changes in human land use (St. Jacques?, maybe not the best. . .).

@@

dissim.scores <- data.frame(dissim = c(min.diss,
                                       as.vector(dists)[sample(length(dists), 10000)]),
                            class   = c(rep('Minimum', length(min.diss)),
                                        rep('All', 10000)))

@@

non.ana.map <- ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_path(aes(group=group), color='black') +
  geom_point(data = data.frame(climate)[mds$non.ana == FALSE,], 
             aes(x = LONDD, y = LATDD), alpha=0.5) +
  geom_point(data = data.frame(climate)[mds$non.ana == TRUE,], 
             aes(x = LONDD, y = LATDD), color = 'red') +
   theme_bw() +
  coord_map(projection='albers', lat0=30, lat1=50, xlim=c(-140, -60), ylim=c(26, 75)) +
  xlab('Longitude') + ylab('Latitude') +
  theme(text = element_text(size=24, family='serif'))

@@

```{r LoadOutputs, echo=FALSE, message=FALSE, warning=FALSE}
load('data/wa.res.RData')
load('data/mat.res.RData')
load('data/wapls.res.RData')
load('data/rfor.res.RData')
load('data/brt.res.RData')

vals <- c(seq(0, 1, by=0.01))
